Hierarchical Reverberation Mapping

### 2013-10-30 Paper/ms.tex
Prior talk

We chose a log-uniform prior for $L$ (the AGN variability timescale)
between $1$ and $10^6$ days, a log-uniform
prior for $\beta$ (the size of the short-term fluctuations)
between $10^{-3}$ and $10^3$ flux units, a Cauchy(0, 100)
prior for $\mu$ (the mean flux level of the AGN), a log-uniform prior for $b$
(the upper limit of the transfer function) between $10^{-3}$ and $10^3$ days,
a uniform prior for $a$ (the lower limit of the transfer function)
between 0 and $b$, a log-uniform prior between
$10^{-3}$ and $10^3$ for the response coefficient $A$ and a Cauchy(0, 100) prior
for the second response parameter $C$.

@@

Finally, we combined the results from the single-object model into an inference
about hyperparameters $\mu$ and $\sigma$ describing the central value and
the diversity of $\bar{\tau}$ respectively, using the result of
Equation~\ref{eq:individual}. Since lags $\bar{\tau}$ are positive, 
our assumption for the prior on $\bar{\tau}$ given
the hyperparameters is a lognormal distribution with median $\mu$ and
width (standard deviation of $\log_{10}(\bar{\tau})$) $\sigma$:
\begin{eqnarray}
\log_{10}(\bar{\tau}) \sim \mathcal{N}(\log_{10}(\mu), \sigma^2)
\end{eqnarray}

>>>>

We used vague priors for the parameters of the single-object model. In practice
these could be made substantially narrower.
We chose a log-uniform prior for $L$ (the AGN variability timescale)
between $0.1$ and $10^5$ days, a log-uniform
prior for $\beta$ (the size of the short-term fluctuations)
between $10^{-3}$ and $10^3$ flux units, a Cauchy(0, 100)
prior for $\mu$ (the mean flux level of the AGN), a log-uniform prior for $b$
(the upper limit of the transfer function) between $10^{-4}$ and $10^2$ days,
a uniform prior for $a$ (the lower limit of the transfer function)
between 0 and $b$, a log-uniform prior between
$10^{-3}$ and $10^3$ for the response coefficient $A$ and a Cauchy(0, 100) prior
for the second response parameter $C$.

@@

Finally, we combined the results from the single-object model into an inference
about hyperparameters $\mu$ and $\sigma$ describing the central value and
the diversity of $\bar{\tau}$ respectively, using the result of
Equation~\ref{eq:individual}. This requires us to know the prior $\pi(\bar{\tau})$
implied by the simple-object model, since we did not assign the prior directly
to $\bar{\tau}$. The prior for $\bar{\tau}$ in the single-object model is
very well approximated by a log-uniform distribution.

Since lags $\bar{\tau}$ are positive, 
our assumption for the prior on $\bar{\tau}$ given
the hyperparameters is a lognormal distribution with median $\mu$ and
width (standard deviation of $\log_{10}(\bar{\tau})$) $\sigma$:
\begin{eqnarray}
\log_{10}(\bar{\tau}) \sim \mathcal{N}(\log_{10}(\mu), \sigma^2)
\end{eqnarray}
